flowCore: data structures package for flow cytometry data

### 2008-11-01 inst/doc/HowTo-flowCore.Rnw
applyParentFilter is gone for good now
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@35030 bc3139a8-67e5-0310-9ffc-ced21a209358

\subsection{Accessing items in the \Rclass{workFlow} object}
The main reason for having the \Rclass{workFlow} class is to be able
to easily access all elements of a potentially complex analysis work
flow. The predominant use case here is to access individual
\Rclass{views}, either for plotting, to create summary statistics or
to use the underlying data for subsequent analysis steps. You can do
that using the familiar list subsetting syntax:
<<getView>>=
wf[["rectangle+"]]
wf$asinh
@
%
This also works for \Rclass{actionItems}:
<<getAction>>=
wf[["action_rectangle"]]
@ 
% 
In order to retreive the underlying data for a \Rclass{view} you
can use the \Rfunction{Data} method.
<<getData>>=
Data(wf[["rectangle+"]])
@ 
%
There are \Rfunction{summary} methods defined for the different
\Rclass{view} subclasses, which basically create the respective
summaries of the associated \Rpackage{flowCore} objects, e.g. a
\Rclass{filterResult} for a filtering operation.
<<summaries>>=
summary(wf[["action_rectangle"]])
summary(wf[["CD15 FITC+CD45 PE+"]])
@ 
The \Rpackage{flowViz} package also defines \Rfunction{xyplot} and
\Rfunction{densityplot} methods for \Rclass{view} objects. Sensible defaults
are usually chosen automatically, for instance to add the gate
boundaries to the plot of a \Rclass{gateView}.
<<plotViews>>=
densityplot(wf[["base view"]])
xyplot(`FL1-H` ~ `FL2-H`, wf[["CD15 FITC+CD45 PE+"]])
@

\subsection{Removing items from \Rclass{workFlow} object}
Still need to document Rm, undo, etc.

>>>>

\subsection{Accessing items in the \Rclass{workFlow} object}
The main reason for having the \Rclass{workFlow} class is to be able
to easily access all elements of a potentially complex analysis work
flow. The predominant use case here is to access individual
\Rclass{views}, either for plotting, to create summary statistics or
to use the underlying data for subsequent analysis steps. You can do
that using the familiar list subsetting syntax:
<<getView>>=
wf[["rectangle+"]]
wf$asinh
@
%
This also works for \Rclass{actionItems}:
<<getAction>>=
wf[["action_rectangle"]]
@ 
% 
In order to retreive the underlying data for a \Rclass{view} you
can use the \Rfunction{Data} method.
<<getData>>=
Data(wf[["rectangle-"]])
@ 
%
There are \Rfunction{summary} methods defined for the different
\Rclass{view} subclasses, which basically create the respective
summaries of the associated \Rpackage{flowCore} objects, e.g. a
\Rclass{filterResult} for a filtering operation.
<<summaries>>=
summary(wf[["action_rectangle"]])
summary(wf[["CD15 FITC+CD45 PE+"]])
@ 
The \Rpackage{flowViz} package also defines \Rfunction{xyplot} and
\Rfunction{densityplot} methods for \Rclass{view} objects. Sensible defaults
are usually chosen automatically, for instance to add the gate
boundaries to the plot of a \Rclass{gateView}.
<<plotViews>>=
densityplot(wf[["base view"]])
xyplot(`FL1-H` ~ `FL2-H`, wf[["CD15 FITC+CD45 PE+"]])
@

\subsection{Removing items from \Rclass{workFlow} object}
The hierarchical structur of the \Rclass{workFlow} object introduces
dependencies between \Rclass{views} or between \Rclass{views} and
\Rclass{actionItems}. Thus, removing a particular view means also
removing all of its associated child \Rclass{views} and
\Rclass{actionItems}. The easiest way to remove objects from a
\Rclass{workFlow} is through the \Robject{undo} mechanism. The
function takes a \Rclass{workFlow} object as first argument and an
optional second integer argument giving the number of operartions that
are supposed to be roled back.
<<undo>>=
undo(wf)
wf
@ 
%
Sometimes it is more convenient to specify a particular \Rclass{view}
or \Rclass{action} item that is to be removed. This can be archived
using the \Rfunction{Rm} methods for \Rclass{views} or
\Rclass{actionItems}. As a side-effect these methods will also remove
all dependent items and the user should be well aware of this
potentially dangerous behaviour.
<<RmView>>=
Rm('rectangle-', wf)
@ 
<<RmAction>>=
Rm('asinh', wf)
@
